---
title: "Lab 3"
output: html_document
---

```{r, loaddata}
songs<-read.csv("http://educ.jmu.edu/~wardex/datasets/spotifytop1000march2019.csv")
head(songs)
```

### Loudness and Popularity
## Scatterplot
```{r, scatterplot}
library(ggplot2)
ggplot(songs, aes(x=loudness, y=popularity))+geom_jitter()+
  geom_smooth(method="lm")
```

## Summary
```{r, sumstats}
summary(lm(loudness~popularity, songs))
```
## DOFS
The slope is -9.50546 with one outlier, Going Bad (feat. Drake). It is linear with a slightly positive relationship. 

## Correlation Coefficient and Coefficient of Determination
```{r, correlation}
cor(songs$loudness, songs$popularity)
cor(songs$loudness, songs$popularity)^2
```
## Regression
```{r, regression}
lm(popularity~loudness, songs)
model1<-lm(popularity~loudness, songs)
summary(model1)
```
The assumptions for hypothesis testing are met. The data is linear, independent, and normally distributed. However, since the correlation is very weak (r=.07), loudness is not a good predictor of popularity. 